\chapter{Source Code}
\localtableofcontents
\newpage
\section{Directory Tree}
\dirtree{%
.1 geranium.
.2 data\_generation.
.3 attacks.
.4 synflood.sh.
.4 udpflood.sh.
.4 finflood.sh.
.4 pshackflood.sh.
.3 traffic-gen.
.3 virtual-machines.
.3 datagen.py.
.3 \_\_init\_\_.py.
.2 data\_processing.
.3 data\_parser.py.
.3 data\_processor.py.
.3 \_\_init\_\_.py.
.2 data\_modeling.
.3 data\_modeling.py.
.3 \_\_init\_\_.py.
.2 intrusion\_detection.
.3 ids.py.
.3 \_\_init\_\_.py.
.2 geranium.py.
.2 config.yaml.
.2 setup.py.
.2 install\_linux.sh.
.2 requirements.txt.
.2 README.md.
.2 test.py
}
\newpage
\chapter*{Originality Avowal}
I verify that I am the sole author of the programs contained in this folder, except where explicitly stated to the contrary.
            \begin{flushright}
        		      \normalsize{Kenan-Ali Jasim}\\*
		      \normalsize{\today}\\*
		      %\normalsize{Word count: \@wordCount}
  		\end{flushright}
\newpage
\section{Geranium}
\subsection{gerainum.py}
\lstinputlisting[language=Python]{Code/geranium.py}
\subsection{setup.py}
\lstinputlisting[language=Python]{Code/setup.py}
\subsection{config.yaml}\label{app:conf}
\lstinputlisting{Code/config.yaml}
\subsection{test.py}
\lstinputlisting[language=Python]{Code/test.py}
\subsection{install\_linux.sh}
\lstinputlisting[language=Python]{Code/installlinux.sh}
\section{Data Generation}
\subsection{datagen.py}
\lstinputlisting[language=Python]{Code/datagen.py}
\subsection{\_\_init\_\_.py}
\lstinputlisting[language=Python]{Code/datageninit.py}
\subsection{attacks/synflood.sh}
\lstinputlisting[language=Shell]{Code/synflood.sh}
\subsection{attacks/synflood\_one.sh}
\lstinputlisting[language=Shell]{Code/synfloodone.sh}
\subsection{attacks/udpflood.sh}
\lstinputlisting[language=Shell]{Code/udpflood.sh}
\subsection{attacks/pshackflood.sh}
\lstinputlisting[language=Shell]{Code/pshackflood.sh}
\subsection{attacks/finflood.sh}
\lstinputlisting[language=Shell]{Code/finflood.sh}
\subsection{traffic-gen}
All code contained in the traffic-gen belongs to Github user ecapuano at \url{https://github.com/ecapuano/web-traffic-generator} and has been used according to the licence supplied which states:

"Permission is hereby granted, free of charge, to any person obtaining a copy
of this software and associated documentation files (the "Software"), to deal
in the Software without restriction, including without limitation the rights
to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the Software is
furnished to do so, subject to the following conditions:"

\section{Data Processing}
\subsection{data\_parser.py}
\lstinputlisting[language=Python]{Code/dataparser.py}
\subsection{data\_processor.py}
\lstinputlisting[language=Python]{Code/dataprocessor.py}
\subsection{\_\_init\_\_.py}
\lstinputlisting[language=Python]{Code/dataprocinit.py}

\section{Data Modeling}
\subsection{data\_modeling.py}
\lstinputlisting[language=Python]{Code/datamodeling.py}
\subsection{\_\_init\_\_.py}
\lstinputlisting[language=Python]{Code/modinit.py}

\section{Intrusion Detection}
\subsection{ids.py}
\lstinputlisting[language=Python]{Code/ids.py}
\subsection{\_\_init\_\_.py}
\lstinputlisting[language=Python]{Code/idsinit.py}